Proportional multi-state multiple-cohort life table model

### 2018-04-27 MSLT/MSLTdoc.Rmd
Updated PDF

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
# require(gridExtra)
# require(cowplot)
# install.packages("ggpubr")
require(ggpubr)
```

>>>>

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(gridExtra)
require(cowplot)
require(ggpubr)
```
